\Title

### 2020-02-18 manuscript/manuscript.tex
Remove unwanted dot

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
to the effect of the synthetic model to simulate acquisition errors.
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

>>>>

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).
